---
title: "Lab 8"
author: "Katie Pietrucha"
date: "11/15/2021"
output: html_document
---

```{r setup, include = TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)
```

## Read in data

```{r}
homes <- read_csv(here("slo_homes.csv"))
```

## A little bit of cleanining

Make a subset called homes_sub that only contains observations (rows) where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt

```{r}
homes_sub <- homes %>%
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt"))
```

## Do a little exploring of our data

Summary statistics (home price, based on city and sale status):

- Find & return in a nice summary table the mean and standard deviation of home price, grouped by city and sale status.

```{r, include = FALSE}
homes_sub_stats <- homes_sub %>%
  group_by(City, Status) %>%
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))

# Actually I don't even want to run this code, use eval = FALSE

ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) +
  scale_x_continuous(limits = c(0, 3e6))
```

Explore the relationship (visual data exploration) between square footage and home price. Change the point COLOR by city, and the point SHAPE by sale status.

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) +
      geom_point(aes(color = City, shape = Status)) +
  geom_smooth(method = lm)
```

## Model the relationship with home price as DV

```{r}
homes_lm1 <- lm(Price ~ City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub)
```

## Check for collinearity

```{r}
# Make a subset that only contains the quantitative variables

homes_sub_quant <- homes_sub %>%
  select(Price:PricePerSqFt)

homes_cor <- cor(homes_sub_quant)

corrplot(homes_cor, method = 'ellipse')

# How would I explore diagnostic plots?

plot(homes_lm1)
```

Try another model where we simplify this a bit: (based on our concerns)

- City
- SqFt
- Status

```{r}
homes_lm2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)

plot(homes_lm2)
```

Results make a lot more sense! but summary() shows that lm1 explains more variance

Find the AIC value of each model:

```{r}
AIC(homes_lm1)
AIC(homes_lm2)
```
Lower value is "better" but maybe neither is great!

Trying another permutation that you think might make sense, check iout & compare the model fit, outputs, and AIC value.

```{r}
homes_lm3 <- lm(Price ~ SqFt + City + Status + Bedrooms, data = homes_sub)

AIC(homes_lm3)
```
Since none are great, it seems like we're missing other variables... lot size? etc.

Use `modelsummary` to show model outputs side-by-side.

If you want to use `modelsummary` to return outputs of multiple models, it wants you to feed it to it as a list.
```{r}
modelsummary(list(homes_lm1, homes_lm2, homes_lm3))
```

## Start making predictions with this model

If only interested in price (not coefficients), first model would work well. But we want both!

Use `broom::augment()`

```{r}
homes_predicted <- augment(homes_lm1)
```

Use the `predict()` function to try out your model on new scenarios that you create.